---
title: 'Presentation of the Application'
author: "Manu"
date: "29/11/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(dplyr)
library(kableExtra)
```

## Introduction

This is a presentation regarding an application developped by the author, named "Diverse information on countries". 

The goal of this App is to demonstrate the capabilities of shiny, with the use of diverse plotly graphs and especially it's capacity related to the integration of **reactive Machine Learning models**.

## Data
The data used come from two main sources, the first one is [Techslides](http://techslides.com/list-of-countries-and-capitals).


```{r dfCap, fig.height = 4, fig.width= 5}
path1 <- ("./final/data/country-capitals.csv") 
df <- read.csv(path1, stringsAsFactors = FALSE)
df <- df %>%
        rename(Country = CountryName) %>%
        rename(Capital = CapitalName) %>%
        rename(Latitude = CapitalLatitude) %>%
        rename(Longitude = CapitalLongitude) %>%
        rename(Continent = ContinentName)

dfTable <- df %>%
        slice_head(n = 5)

dfTable %>%
        kable(format = "html", escape = FALSE, align = c("l", "c", "c", "c", "c", "c")) %>%
        kable_styling(bootstrap_options = c("striped", "hover", "responsive"))

```

## Summary of the data

```{r df, echo = TRUE}
summary(df)
```


## Data
The second source is [World Bank](https://datacatalog.worldbank.org/).

```{r dfPop, fig.height = 4, fig.width= 5}
path1 <- ("./final/data/gdpPop.csv") 
dfPop <- read.csv(path1, stringsAsFactors = FALSE)
dfPop <- dfPop %>%
        rename(Year = ï..year) %>%
        rename(Code = countryCode) %>%
        rename(Mil.exp = militaryExpenditure) %>%
        rename(Country = country) %>%
        rename(GDP = gdp) %>%
        rename(Population = population)

dfPopTable <- dfPop %>%
        slice_head(n = 5)

dfPopTable %>%
        kable(format = "html", escape = FALSE, align = c("l", "c", "c", "c", "c", "c")) %>%
        kable_styling(bootstrap_options = c("striped", "hover", "responsive"))


```
## Summary of the data

```{r wbank, echo = TRUE}
summary(dfPop)
```

## Link to the application
Having now the data in mind, I encourage you to try and and use the application by clicking on the following link: [Diverse information on countries](https://manuaccount.shinyapps.io/testDispo/).

The server.R and ui.R code have been stored on [github] if needed

Thank you very much for your attention !

